\chapter*{Acknowledgment}     % Won't show up in the table of content
%

I would like to express my gratitude to the many people that helped me during my work on this Master Thesis.

\begin{itemize}

\item I would like to thanks Prof. Hans Zappe for providing the opportunity to work on such an interesting and engaging project. But also for the inspiration and energy that he conveyed since the first class of Microoptics and kept through each meeting and trip, as well as for the hilarious and helpful \textit{How to write a thesis} guide. 

\item I would also like to thanks Prof. Alexander Rohrbach as the second referee, but also for his outstanding lecture in \textit{Photonic Microscopy}. Without the intuition that I acquired during this lecture, this project wouldn't have been as insightful.

\item A special thanks to Simon Kretschmer for the endless reviews of this thesis, coaching, guiding, mentoring, encouragement and psychological advice. But mostly for being a constant example of hard work and engineering carefulness. Not to forget his help in my first steps in the cleanroom.

\item Çağlar Ataman, as group leader, for introducing me to this project and for pushing and guiding it in every meeting, for all the brilliant solutions that kept the project running after each difficult moment and again for the example of hard work.

\item Bilal Khatri, from the \textit{Laboratory for Materials Processing} for always keeping a smile regardless of the uncountable manufacturing iterations of the 3D printed housing of the probe.

\item The \textit{Laboratory for the Design of Microsystems} for the first prototypes of the 3D printed housing.

\item The \textit{Leitgeb Lab} team, including Rainer A. Leitgeb, Lara Wurster and Zhe Chen for the invaluable help during the long experiments in the \textit{Medical University of Vienna}.

\item Marc Blattmann for the guidance and motivation during my first months in the lab.

\item Kaustubh Banerjee for the mathematical and linguistic discussions during this thesis.

\item Bernd Aatz for the kind help in the machining of the assembly tools and for keeping the good mood in this Chair.

\item All the micro-opticians for the enjoyable time working on the thesis and for the outstanding quality of work that I have seen in every thesis and publication from this Chair.

\item The \textit{Mensa Food Quality Research Lab}, specially Salvador Aguilar, Hai Phan, Mariã Joao Sousa, Zoltán Daniló and Gerardo Gonzalez for the therapeutical effect of our random conversations during lunch.

\item A toda mi familia y amigos, por el apoyo que me dais cada vez que nos vemos por la pantalla del ordenador o visito España. 

\item And finally, thanks to the 522 cups of coffee, 620 cups of tea, 127 chocolate bars and 13244 songs from Spotify during the last 14 months. Without you, this thesis would have been unbearable.
\end{itemize}

Thank you!